Setup Honeypot: Team Contagiarium

### 2011-11-01 Setup_honeypot.tex
Fixed denyhosts onzin
added wordpress and editted iptables

@@

\subsection{DenyHosts}
If someone finds out our real SSH port changed to 9022, they might try to break in through our real SSH service.
To make sure no bruteforce attacks can be done on this port, DenyHosts is installed.
This service blocks IP-addresses that try to log in more than 3 times with the wrong password by adding them to the \verb|hosts.deny| file.
The hosts listed there are blacklisted on the machine, but we can edit them if needed.

This does not log to syslog. We hope to fix that, but it's not a priority until the HI phase.

@@

>>>>

We are also going to filter outgoing SMTP, SIP and NetBIOS.

@@

\subsection{DenyHosts}
If someone finds out our real SSH port changed to 9022, they might try to break in through our real SSH service.
To make sure no bruteforce attacks can be done on this port, DenyHosts is installed.
This service blocks IP-addresses that try to log in more than 3 times with the wrong password by adding them to the \verb|hosts.deny| file.
The hosts listed there are blacklisted on the machine, but we can edit them if needed.
Denyhosts can log to syslog by editing its configuration file.

@@

We also hope to detect and capture a bruteforce attack or scan on generic filenames, for example \verb|passwd.txt|. 
This will probably warn us that an attacker will try to use a dictionary attack.

\subsection{Wordpress}

To capture more attackers during the HI phase, we plan to use an outdated version of WordPress. 
Wordpress is software, powered by PHP and MySQL, that can be used to easily create websites or blogs and manage them via the content management system. 
Unfortunately exploits are frequently found for Wordpress and patches are published on a regular basis. 
We plan to use an older version of Wordpress, for example a version below version 3.0.4, to be sure that we use a version with some exploits.
